\chapter*{Preface\markboth{Preface}{Preface}}\label{ch:preface}
\addcontentsline{toc}{chapter}{Preface}
This thesis has been written by Tomas B. Trillingsgaard, who is a student at the Signal Processing and Computing Master's Program, Aalborg University. The thesis serves as documentation for the authors master project, which have been devised in the period from February 1 to September 30, 2016. The theme for this project is \textit{Signal Processing and Computering} where the subject \textit{Implementation of a stereo vision engine} is chosen.

\section*{Reading Instructions}
The thesis is addressed to supervisors, students and other with interest in the field of Electronics and Information Technology. By extension the thesis presumes the reader have a basic knowledge within this field. \\

The thesis contains references following the IEEE citation style; [i]. These references points to the bibliography in the back of the thesis on page \pageref{bib:mybiblio}. The bibliography contains information about the source like author, title, year of release, etc.\\

Figures and tables are numbered according to the location in the thesis. List of figures and tables can be also be found in the back of the thesis on \pageref{bib:mybiblio}. Unless otherwise described, the figures and tables in the thesis have been produced by the author. When referring to these, their numbers will be used which will be followed the location if they are not on the same page.\\

Formulas and calculations are also numbered according to their location and referenced to in the same way as figures and tables.

\vspace{\baselineskip}\hfill Aalborg University, \today
\vfill\noindent
\begin{center}
\begin{minipage}[b]{0.45\textwidth}
 \centering
 \rule{\textwidth}{0.5pt}
  Tomas Brandt Trillingsgaard\\
 {\footnotesize <ttrill10@student.aau.dk>}
\end{minipage}
\end{center}
